### 2017-02-07 readme.Rmd
readme me update

Generate some random points and a raster to represent study area.
```{r}
library(raster)
N <- 100
ks <- as.data.frame(cbind(x1=runif(N, min=-10, max=10),x2=runif(N, min=-10, max=10)))
sa <- raster(nrows=100, ncols=100, xmn=-10, xmx=10,ymn=-10,ymx=10)
sa[]<-rnorm(10000)
projection(sa) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
plot(sa)
points(ks$x1,ks$x2,pch=16,add=TRUE)
```

How many qausiRandom background points do we need?
```{r}
library(qrbp)
set.seed(123)
n <- 200
bkpts <- qrbp(n,dimension = 2,known.sites=ks,include.known.sites=TRUE,
              study.area = sa,inclusion.probs = NULL,sigma=1,plot.prbs=TRUE)
```

>>>>

Generate some random points and a raster to represent study area.
```{r}
library(raster)
N <- 100
ks <- as.data.frame(cbind(x1=runif(N, min=-10, max=10),x2=runif(N, min=-10, max=10)))
sa <- raster(nrows=100, ncols=100, xmn=-10, xmx=10,ymn=-10,ymx=10)
sa[]<-rnorm(10000)
projection(sa) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
plot(sa)
points(ks$x1,ks$x2,pch=16)
```

How many qausiRandom background points do we need? Let start with 200.
The function will plot the underlying probability of sampling intensity, the presence points (white) amd the generated quasi-random background points.
```{r}
library(qrbp)
set.seed(123)
n <- 200
bkpts <- qrbp(n,dimension = 2,known.sites=ks,include.known.sites=TRUE,
              study.area = sa,inclusion.probs = NULL,sigma=1,plot.prbs=TRUE)
points(ks$x1,ks$x2,pch=16,col='white')
```
